The regularity of ODEs and thimble integrals \\ with respect to Borel summation \begin{draft}\textbf{[DRAFT]}\end{draft}

### 2024-06-02 exp-resurgence.tex
Revise intro to thimble integral results

\subsection{Goals and Results}
%
We present the results, proofs, and examples in this paper with a few central goals in mind. Our first goal is to discuss Borel summability in a way that carefully separates the analytic and formal sides of the theory. In particular, we highlight results---like Theorem~\ref{thm:exist_uniq_ODE} for level~1 ODEs and Lemma~\ref{lem:thimble_proj_formula} for thimble integrals---that can be proven in purely analytic ways.

@@

\begin{todo}[Plentiful, novel examples.]\end{todo}
\begin{old}\par
First of all, we want to clearly separate the parts of the theory that deal with holomorphic functions and formal series. For ODEs, we proved in \cite[Theorem~4]{reg-sing-volterra} how to build an analytic frame of solutions with an explicit growth behavior, while for thimble integrals we will prove in part 3 of Theorem~\ref{thm:maxim} that there is an explicit analytic function whose Laplace transform is the thimble integral itself. \textcolor{Maroon}{[In other words, we go directly from the frequency--analytic quadrant to the position--analytic quadrant, without passing through the formal side.]}

@@

Given a translation chart $\zeta$ on a translation surface $B$, we write $\mathcal{J}_{\zeta, \alpha}^\theta$ to denote the ray in direction $\theta$ starting at $\zeta = \alpha$. Consider a map $f \maps X \to B$ with a critical value at $\zeta = \alpha$. Each connected component of the preimage $f^{-1}(\mathcal{J}_{\zeta, \alpha}^\theta)$ runs through one of the critical points that $f$ sends to $\zeta = \alpha$. When the complex manifold $X$ is one-dimensional, as it will be throughout this paper, a {\em Lefschetz thimble} is an oriented component of $f^{-1}(\mathcal{J}_{\zeta, \alpha}^\theta)$ that runs through a single, non-degenerate critical point of $f$. A one-dimensional Lefschetz thimble is determined up to orientation by the critical point $a$ that it runs through and the direction $\theta$ of the ray that it projects to, so we will often denote it with a symbol like $\mathcal{C}^\theta_a$.
\begin{center}
\includegraphics[width=6.5cm]{figures/rays_ge6.png}
\hspace{0.5cm}
\includegraphics[width=6.5cm]{figures/thimbles-n5.png}
\captionof{figure}{On the left, we see the rays $\mathcal{J}^{\pi/8}_{\zeta, \pm 1}$ on the translation surface $B = \C$, where $\zeta$ is the standard coordinate. On the right, we see the complex manifold $X = \C$, colored according to a holomorphic map $f \maps X \to B$ whose critical values are $\zeta = \pm 1$. The Lefschetz thimbles over the rays $\mathcal{J}^{\pi/8}_{\zeta, \pm 1}$ are shown.}
\end{center}
%%
%%supposing for the moment that $X$ is an $N$-dimensional complex manifold.
%%
%%Each connected component of the preimage $f^{-1}(\mathcal{J}_{\zeta, \alpha}^\theta)$ runs through a critical point of $f$. When {\em Lefschetz thimble} is a component that runs through a non-degenerate critical point.
%%
%%To \textcolor{orange}{[\ldots]}, consider a non-degenerate critical point $a$ in the preimage of $\zeta = \alpha$, and let $\mathcal{C}^\theta_a$ be the Lefschetz thimble that runs through it. Near $a$ we can always find coordinates $t_1, \ldots, t_N$ on $X$ with $f = t_1^2 + \ldots + t_N^2$.
%%
%%To see why the term ``thimble'' is fitting, consider a non-degenerate critical point $a$ in the preimage of $\zeta = \alpha$, and let $\mathcal{C}^\theta_a$ be the Lefschetz thimble that runs through it. Near $a$ we can always find coordinates $x_1, \ldots, x_N$ on $X$ in which $\mathcal{C}^\theta_a$ looks like the paraboloid
%%where $\zeta = \alpha + \zeta_\alpha$. \textcolor{orange}{[\ldots]}

@@

\begin{todo}[\textbf{A} \textbf{V} Check whether anything from the old text is missing from the revised text.]\end{todo}

@@

Consider a thimble integral of the form described in Section~\ref{borel-reg:explanatory-power}. We will define our setting in the language of translation surfaces, to make clear the connection with our geometric picture of the Laplace transform. The codomain of $f$ has a natural structure of translation surface---a Riemann surface carrying a holomorphic 1-form $d\zeta$, and $\zeta$ is a translation coordinate. \textcolor{NavyBlue}{[The important thing about $\C$, where $f$ takes values, is that it is a translation surface---\ldots]} For each critical point $a$, let $\mathcal{J}_\alpha^\theta$ be the ray going to infinity with an angle $\theta$ from the critical value $\alpha$, and let $\zeta_{\alpha}$ be the translation coordinate around $\mathcal{J}_\alpha^\theta$ which vanishes at $\alpha$. These are well-defined as long as $\mathcal{J}_\alpha^\theta$ misses the critical values of $f$. Then, the preimage $f^{-1}(\mathcal{J}_\alpha^\theta)$ is a bunch of disjoint curves (see Figure \ref{fig:thimble_vs_rays}), as long as $\mathcal{J}_\alpha^\theta$ misses the other critical values of $f$. The Lefschetz thimble $\mathcal{C}_a^\theta$ can be regarded as the component of $f^{-1}(\mathcal{J}_\alpha^\theta)$ that goes through $a$. \textcolor{orange}{We could orient the thimble so that shifting $\mathcal{C}_a$ to its left would make its projection run clockwise around $\mathcal{J}_\alpha$. However, this only seems to be possible when $X$ is 1-dimensional.} 

@@

Choose a critcal point $a$ of $f$, noting the associated critical value $\alpha = f(a)$, and let $I_\alpha$ be a thimble integral through the thimble $\mathcal{C}_a^\theta$:

@@

\begin{draft}Our main results show that $I_a$ is Borel regular as a conseuqence of the fact that thimble integrals can be turned into a Laplace transform on the ray $f(\mathcal{C}_a^\theta)$. \begin{todo}[no need to say more; just get to the results]\end{todo}. \begin{todo}[As a start\ldots\end{todo} We recall the well-known result\end{draft}

@@

@@

\begin{todo}\textbf{A} [Use $a$ subscript instead of $\alpha$ for $I$ and $\iota$.]\end{todo} Since $f$ has non--degenerate critical points, we can find a holomorphic chart $\tau$ around $a$ with $\tfrac{1}{2} \tau^2 = f - f(a)$. Let $\mathcal{C}^-_a$ and $\mathcal{C}^+_a$ be the parts of $\mathcal{C}_a^\theta$ that go from the past ($-e^{-i\theta}\infty$) to $a$ and from $a$ to the future ($+e^{-i\theta}\infty$), respectively. By changing the sign of $\tau$, we can arrange for it to be valued in $(-\infty, 0]$ and $[0,\infty)$ on $\mathcal{C}^-_a$ and $\mathcal{C}^+_a$, respectively. Since $\nu$ is holomorphic, we can express it as a Taylor series

>>>>

\subsection{Goals and Results}
%
We present the results, proofs, and examples in this paper with a few central goals in mind. Our first goal is to discuss Borel summability in a way that carefully separates the analytic and formal sides of the theory. In particular, we highlight results that can be proven in purely analytic ways, like Theorem~\ref{thm:exist_uniq_ODE} for level~1 ODEs and Lemma~\ref{lem:thimble_proj_formula} for thimble integrals.

@@

\begin{todo}[Plentiful, novel examples.]\end{todo} Our third goal is to
\begin{old}\par
First of all, we want to clearly separate the parts of the theory that deal with holomorphic functions and formal series. For ODEs, we proved in \cite[Theorem~4]{reg-sing-volterra} how to build an analytic frame of solutions with an explicit growth behavior, while for thimble integrals we will prove in part 3 of Theorem~\ref{thm:maxim} that there is an explicit analytic function whose Laplace transform is the thimble integral itself. \textcolor{Maroon}{[In other words, we go directly from the frequency--analytic quadrant to the position--analytic quadrant, without passing through the formal side.]}

@@

Given a translation chart $\zeta$ on a translation surface $B$, we write $\mathcal{J}_{\zeta, \alpha}^\theta$ to denote the ray in direction $\theta$ starting at $\zeta = \alpha$. Consider a map $f \maps X \to B$ with a critical value at $\zeta = \alpha$. Each connected component of the preimage $f^{-1}(\mathcal{J}_{\zeta, \alpha}^\theta)$ runs through one of the critical points that $f$ sends to $\zeta = \alpha$. When the complex manifold $X$ is one-dimensional, as it will be throughout this paper, a {\em Lefschetz thimble} is an oriented component of $f^{-1}(\mathcal{J}_{\zeta, \alpha}^\theta)$ that runs through a single, non-degenerate critical point of $f$. A one-dimensional Lefschetz thimble is determined up to orientation by the critical point $a$ that it runs through and the direction $\theta$ of the ray that it projects to, so we will often denote it with a symbol like $\mathcal{C}^\theta_a$. \begin{revised}Because a Lefschetz thimble can only run through a single critical point $a$, the ray that it projects to cannot touch any critical value except $f(a)$.\end{revised}
\begin{center}
\includegraphics[width=6.5cm]{figures/rays_ge6.png}
\hspace{0.5cm}
\includegraphics[width=6.5cm]{figures/thimbles-n5.png}
\captionof{figure}{On the left, we see the rays $\mathcal{J}^{\pi/8}_{\zeta, \pm 1}$ on the translation surface $B = \C$, where $\zeta$ is the standard coordinate. On the right, we see the complex manifold $X = \C$, colored according to a holomorphic map $f \maps X \to B$ whose critical values are $\zeta = \pm 1$. The Lefschetz thimbles over the rays $\mathcal{J}^{\pi/8}_{\zeta, \pm 1}$ are shown.}
\end{center}
%%
%%supposing for the moment that $X$ is an $N$-dimensional complex manifold.
%%
%%Each connected component of the preimage $f^{-1}(\mathcal{J}_{\zeta, \alpha}^\theta)$ runs through a critical point of $f$. When {\em Lefschetz thimble} is a component that runs through a non-degenerate critical point.
%%
%%To \textcolor{orange}{[\ldots]}, consider a non-degenerate critical point $a$ in the preimage of $\zeta = \alpha$, and let $\mathcal{C}^\theta_a$ be the Lefschetz thimble that runs through it. Near $a$ we can always find coordinates $t_1, \ldots, t_N$ on $X$ with $f = t_1^2 + \ldots + t_N^2$.
%%
%%To see why the term ``thimble'' is fitting, consider a non-degenerate critical point $a$ in the preimage of $\zeta = \alpha$, and let $\mathcal{C}^\theta_a$ be the Lefschetz thimble that runs through it. Near $a$ we can always find coordinates $x_1, \ldots, x_N$ on $X$ in which $\mathcal{C}^\theta_a$ looks like the paraboloid
%%where $\zeta = \alpha + \zeta_\alpha$. \textcolor{orange}{[\ldots]}

@@

\begin{todo}[\textbf{V} Check whether anything from the old text is missing from the revised text.]\end{todo}

@@

\begin{todo}[A: nothing in this paragraph is missing]\end{todo} Consider a thimble integral of the form described in Section~\ref{borel-reg:explanatory-power}. We will define our setting in the language of translation surfaces, to make clear the connection with our geometric picture of the Laplace transform. The codomain of $f$ has a natural structure of translation surface---a Riemann surface carrying a holomorphic 1-form $d\zeta$, and $\zeta$ is a translation coordinate. \textcolor{NavyBlue}{[The important thing about $\C$, where $f$ takes values, is that it is a translation surface---\ldots]} For each critical point $a$, let $\mathcal{J}_\alpha^\theta$ be the ray going to infinity with an angle $\theta$ from the critical value $\alpha$, and let $\zeta_{\alpha}$ be the translation coordinate around $\mathcal{J}_\alpha^\theta$ which vanishes at $\alpha$. These are well-defined as long as $\mathcal{J}_\alpha^\theta$ misses the critical values of $f$. Then, the preimage $f^{-1}(\mathcal{J}_\alpha^\theta)$ is a bunch of disjoint curves (see Figure \ref{fig:thimble_vs_rays}), as long as $\mathcal{J}_\alpha^\theta$ misses the other critical values of $f$. The Lefschetz thimble $\mathcal{C}_a^\theta$ can be regarded as the component of $f^{-1}(\mathcal{J}_\alpha^\theta)$ that goes through $a$. \textcolor{orange}{We could orient the thimble so that shifting $\mathcal{C}_a$ to its left would make its projection run clockwise around $\mathcal{J}_\alpha$. However, this only seems to be possible when $X$ is 1-dimensional.} 

@@

\begin{todo}[A: nothing in this paragraph is missing]\end{todo} Choose a critcal point $a$ of $f$, noting the associated critical value $\alpha = f(a)$, and let $I_\alpha$ be a thimble integral through the thimble $\mathcal{C}_a^\theta$:

@@

\begin{draft}Our main results show that $I_a$ is Borel regular as a conseuqence of the fact that thimble integrals can be turned into a Laplace transform on the ray $f(\mathcal{C}_a^\theta)$. \begin{todo}[no need to say more; just get to the results]\end{todo}. \begin{todo}[As a start\ldots\end{todo} We recall the well-known result\end{draft}\par
\begin{revised}We will present a proof that one-dimensional thimble integrals are always Borel regular. The proof hinges on the following well-known formula, which can be used to express any one-dimensional thimble integral as a Laplace transform.\end{revised}

@@

   \textbf{V} temptative proof
   First we notice that the convolution product can be rewritten by introducing the parameter $s\in [0,1]$
       \phi \ast_{\zeta, \alpha} \psi &= \int_{\substack{\mathcal{S}'(\zeta) \times \mathcal{S}''(\zeta) \\ \zeta' + \zeta'' = \zeta}} \phi'\,\psi''\,d\zeta''\\
       &=\zeta_\alpha\,\int_0^1 \phi' \psi''\,ds\,,
   where $\zeta'=s\zeta_\alpha+\alpha$ and consequently $\zeta''=\zeta_\alpha (1-s)$. Then, the Laplace transform of $\phi \ast_{\zeta, \alpha} \psi$ reads
       \laplace_{\zeta,\alpha}[{\phi}\ast_{\zeta, \alpha}{\psi}]&=e^{-z\alpha}\laplace_{\zeta_\alpha,0}[{\phi}\ast_{\zeta, \alpha}{\psi}]\\
       &=e^{-z\alpha}\int_{\Gamma_{\zeta_\alpha,0}}d\zeta_\alpha\,e^{-z\zeta_\alpha}\zeta_\alpha\, \int_0^1 \phi' \psi''\,ds \\
       &=e^{-z\alpha}\int_{\Gamma_{\zeta_\alpha,0}}d\zeta_\alpha\, \int_0^1 \zeta_\alpha\,e^{-z\zeta_\alpha(1-s)} e^{-z\zeta_\alpha s} \phi' \psi''\,ds 
   by exchanging the order of integration we find 
        &=\int_0^1 ds\,\int_{\Gamma_{\zeta_\alpha,0}}d\zeta_\alpha\,\zeta_\alpha\,e^{-z\zeta_\alpha(1-s)} e^{-z(\zeta_\alpha s+\alpha)} \phi' \psi'' \\
        &=\int_0^1 ds\,\int_{\Gamma_{\zeta'',0}}d\zeta''\,\frac{\zeta''}{(1-s)^2}\,e^{-z\zeta''} e^{-z(\zeta'' \frac{s}{1-s}+\alpha)} \phi' \psi'' 
   Exchanging one more time the order of integration we get
        &=\int_{\Gamma_{\zeta'',0}}d\zeta'' \,e^{-z\zeta''}  \psi'' \,\int_0^1 ds\,\frac{\zeta''}{(1-s)^2}e^{-z(\zeta'' \frac{s}{1-s}+\alpha)} \phi'\\
        &=\int_{\Gamma_{\zeta'',0}}d\zeta'' \,e^{-z\zeta''}  \psi'' \,\int_{\Gamma_{t,0}} dt\, e^{-zt} \phi\\
   where we have introduced the coordinate $t=\zeta''\frac{s}{1-s}+\alpha$ which gives the ray $\Gamma_{t,0}$ as $s$ varies in $[0,1]$.

@@

\begin{todo}\textbf{V} [Check that $\alpha$ subscripts have been converted to $a$ for $I$, $\iota$, and $\mathcal{C}$.]\end{todo} Since $f$ has non--degenerate critical points, we can find a holomorphic chart $\tau$ around $a$ with $\tfrac{1}{2} \tau^2 = f - f(a)$. Let $\mathcal{C}^-_a$ and $\mathcal{C}^+_a$ be the parts of $\mathcal{C}_a^\theta$ that go from the past ($-e^{-i\theta}\infty$) to $a$ and from $a$ to the future ($+e^{-i\theta}\infty$), respectively. By changing the sign of $\tau$, we can arrange for it to be valued in $(-\infty, 0]$ and $[0,\infty)$ on $\mathcal{C}^-_a$ and $\mathcal{C}^+_a$, respectively. Since $\nu$ is holomorphic, we can express it as a Taylor series
